# Homework 3

Read in dataset

```{r}
load("hw2_list.rda")
```

Create objects

```{r}
t_df <- bp_list$treatment
p_df <- bp_list$placebo
```

## Task 1

1.  Add new status column to both data frames within the bp_list

```{r}
bp_list$treatment$status <- character(20) 
```

```{r}
bp_list$placebo$status <- character(10) 
```

2.  Add values to new 'status' columns

```{r}
t_df$status <- ifelse(t_df$post_bp <= 120,"Optimal",
                               ifelse(t_df$post_bp>120 & t_df$post_bp <=130, "Borderline",
                                      ifelse(t_df$post_bp>130, "High",NA)))
```

```{r}
p_df$status <- ifelse(p_df$post_bp <= 120,"Optimal",
                               ifelse(p_df$post_bp>120 & p_df$post_bp <=130, "Borderline",
                                      ifelse(p_df$post_bp>130, "High",NA)))

```

## Task 2

1.Create a function a. takes in a list with two data frames in it (a treatment and a placebo data frame) as an argument.

```{r}
sum_stat <- function(data_list) {
  treatment <- data_list$treatment
  placebo <- data_list$placebo
}
```

b.  takes in an R function (that would find a summary of a numeric column) with the default value being set to "mean" (notice this is a quoted string).

```{r}
sum_stat <- function(data_list, stat = "mean") {
  treatment <- data_list$treatment
  placebo <- data_list$placebo
}
```

c.  Finds the statistic of interest (as defined by the user input) for the pre, post, and diff columns of both data frames. – Use my_fun \<- get(stat) within the function to get the function from the quoted string.

```{r}
sum_stat <- function(data_list, stat = "mean") {
  treatment <- data_list$treatment
  placebo <- data_list$placebo
my_fun <- get(stat)
  treatment_pre <- my_fun(treatment$pre)
  treatment_post <- my_fun(treatment$post)
  treatment_diff <- my_fun(treatment$diff)
  
  placebo_pre <- my_fun(placebo$pre)
  placebo_post <- my_fun(placebo$post)
  placebo_diff <- my_fun(placebo$diff)
}
```

d.  These six values should then be returned as a named list with meaningful names - this is a somewhat challenging part!

```{r}
sum_stat <- function(data_list, stat = "mean") {
  treatment <- data_list$treatment
  placebo <- data_list$placebo
my_fun <- get(stat)
  treatment_pre <- my_fun(treatment$pre)
  treatment_post <- my_fun(treatment$post)
  treatment_diff <- my_fun(treatment$diff)
  
  placebo_pre <- my_fun(placebo$pre)
  placebo_post <- my_fun(placebo$post)
  placebo_diff <- my_fun(placebo$diff)
  
  values <- c(treatment_pre, treatment_post, treatment_diff, placebo_pre, placebo_post, placebo_diff)
  
  names(values) <- c(paste0("treatment_", c("pre_", "post_", "diff_"), stat),
                     paste0("placebo_", c("pre_", "post_", "diff_"), stat))
  
    return(values)
}
```

e.  Finally, apply your function to you list of data frames from previous. Use it without specifying your statistic, with specifying your statistic as "var", "sd", "min", and "max".

```{r}
sum_stat(bp_list)
```

```{r}
sum_stat(bp_list, stat = "var")
```

```{r}
sum_stat(bp_list, stat = "sd")
```

```{r}
sum_stat(bp_list, stat = "min")
```

```{r}
sum_stat(bp_list, stat = "max")
```
